GA-based Training-Free NAS Algorithm with Hybrid Score Function

### 2023-03-12 paper/main.tex
update related work section

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
%\documentclass[sigconf]{acmart}
%\let\Bbbk\relax %% fix bug
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{url}
\usepackage{indentfirst}
\usepackage{comment}
\usepackage{algorithm}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{amsopn}
\usepackage{algpseudocode}

\title{GA-based Training-Free NAS Algorithm with Hybrid Score Function}
\author{Hsieh Cheng-Han}
\date{2023}

@@

\maketitle

\section{Abstract}

@@

\section{Introduction}

% introduction
    Neural architecture search (NAS) has recently drawn a big amount of 
    attention, since the ability to automatically design a "good" neural 
    architecture. By leveraging machine learning algorithms (Zoph \& Le,
    \ \cite{https://doi.org/10.48550/arxiv.1611.01578}), NAS algorithms 
    can explore a search space, which is comprised of numerous potential 
    architectures, to find out a good architectures that outperform those 
    designed by human experts. In recent years, the use of NAS is widespread, 
    from object detection (Sun et al.,\ \cite{https://doi.org/10.48550/arxiv.2111.13336}), 
    image recognition (Mellor et al.,\ \cite{https://doi.org/10.48550/arxiv.2006.04647}) 
    and speech recognition (Zheng et al.,\ \cite{https://doi.org/10.48550/arxiv.2011.05649}, 
    Mehrotra et al.,\ \cite{mehrotra2021nasbenchasr}) to natural language 
    processing(Jiang et al.,\ \cite{jiang-etal-2019-improved}, 
    Klyuchnikov et al.,\ \cite{https://doi.org/10.48550/arxiv.2006.07116}, 
    Wang et al.,\ \cite{https://doi.org/10.48550/arxiv.2005.14187}).

@@

    To overcome this challenge, recent works developed and proposed lots 
    of method which is so called training-free NAS. Some use mean absolute 
    error random sampling (MRS) (Camero et al.,\ \cite{https://doi.org/10.48550/arxiv.1805.07159}, 
    Camero et al.,\ \cite{Camero_2021}, Camero et al.,\ \cite{https://doi.org/10.48550/arxiv.2106.15295}) 
    as a training-free score function and some use neural tangent kernel 
    (NTK) (Chen et al.,\ \cite{https://doi.org/10.48550/arxiv.2102.11535}, 
    Wang et al.,\ \cite{https://doi.org/10.48550/arxiv.2203.09137}, 
    Shu et al.,\ \cite{https://doi.org/10.48550/arxiv.2109.00817}), while 
    some use gradient-based methods (Zhang \& Jia,\ \cite{https://doi.org/10.48550/arxiv.2110.08616}, 
    Cavagnero et al.,\ \cite{https://doi.org/10.48550/arxiv.2207.05135}, 
    Abdelfattah et al.,\ \cite{https://doi.org/10.48550/arxiv.2101.08134}).

@@

% method
    Based on the fact above, we propose cooperating three heterogeneous score 
    functions with genetic-based search method, we shall evaulate an architecture 
    from different aspects. More specifically, the first score function is 
    noise immunity for neural architecture search without training (NINASWOT) 
    (Wu et al.\ \cite{10.1145/3491396.3506510}). Starting with the work of Mellor 
    et al., they proposed the measurement of the correlation between binary 
    activation paterns of input data at each ReLU layer, named as neural architecture 
    search without training (NASWOT). Later, Wu et al. found a high score obtained 
    by such a function may not correspond to a high-performence model. Thus, 
    they additionally applied noisy immunity method on NASWOT, named as NINASWOT. 
    Second one is maximum-entropy detection (MAE-DET) (Sun et al.\ \cite{https://doi.org/10.48550/arxiv.2111.13336}). 
    Based on the work of Sun et al., they proposed to find the maximum of 
    the differential entropy by calculating the variance of the output at 
    the final layer with the input Gaussian noise images and random weights on 
    Gaussian distribution. Third one is condition number of neural tangent kernel 
    (NTK) (Chen et al.\ \cite{https://doi.org/10.48550/arxiv.2102.11535}), which is 
    defined as 
    \begin{equation}
        \mathcal{K_N}=\frac{\lambda_{\textrm{max}}(\hat\Theta)}{\lambda_{\textrm{min}}(\hat\Theta)}
    \end{equation}
    Chen et al. used the condition number of NTK as the score to estimate the performance of an architecture.

% results
    The simulation results on cifar-10, cifar-100, and ImageNet-16-120 
    shall show that the proposed method can find good architectures in 
    reasonable time and computational resource. (TODO)

% conclusion
    The major contribution of this paper can be summarized as follow:
    \begin{itemize}
        \item Develope a genetic-based neural architecture search method based on three hybrid score function.
        \item (TODO)
    \end{itemize}

@@

>>>>

%\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
\documentclass[sigconf]{acmart}
\let\Bbbk\relax %% fix bug
\usepackage[utf8]{inputenc}

% =======================
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{amsopn}
%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}

\usepackage{textcomp}

\usepackage{boxedminipage}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{url}
\usepackage{times}
\usepackage{version}
% \usepackage[pdftex]{graphicx}
\usepackage{epsfig}
\usepackage{epsf}
%\usepackage{graphics}
\usepackage{caption}
\usepackage{subfigure}
\usepackage{algorithm}
\usepackage{algpseudocode}
%\PassOptionsToPackage{bookmarks={false}}{hyperref}
%%%%%%%%%%%%
\usepackage{comment}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{dblfloatfix}
% ==========================
\input lstset.tex
\input macros.tex

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

\title{GA-based Training-Free NAS Algorithm with Hybrid Score Function}

\author{Hsieh Cheng-Han}
\email{emiliaistruelove@gmail.com}
\affiliation{%
  \institution{Department of Computer Science and Engineering, National Sun Yat-sen University}
  \streetaddress{70 Lienhai Rd}
  \city{Kaohsiung}
  \country{Taiwan}
}

\author{Chun-Wei Tsai}
\email{cwtsai@mail.cse.nsysu.edu.tw}
\affiliation{%
  \institution{Department of Computer Science and Engineering, National Sun Yat-sen University}
  \streetaddress{70 Lienhai Rd}
  \city{Kaohsiung}
  \country{Taiwan}
}

\begin{abstract}

@@

\end{abstract}
\maketitle

\section{Introduction}
\label{sec:introduction}

% introduction
    Neural architecture search (NAS) has recently drawn a big amount of 
    attention, since the ability to automatically design a "good" neural 
    architecture. By leveraging machine learning algorithms \cite{https://doi.org/10.48550/arxiv.1611.01578}, 
    NAS algorithms can explore a search space, which is comprised of numerous 
    potential architectures, to find out a good architectures that outperform 
    those designed by human experts. In recent years, the use of NAS is 
    widespread, from object detection \cite{https://doi.org/10.48550/arxiv.2111.13336}, 
    image recognition \cite{https://doi.org/10.48550/arxiv.2006.04647} 
    and speech recognition \cite{https://doi.org/10.48550/arxiv.2011.05649} 
    \cite{mehrotra2021nasbenchasr} to natural language 
    processing. \cite{jiang-etal-2019-improved} 
    \cite{https://doi.org/10.48550/arxiv.2006.07116} 
    \cite{https://doi.org/10.48550/arxiv.2005.14187}

@@

    To overcome this challenge, recent works developed and proposed lots 
    of method which is so called training-free NAS. 
    % NINASWOT
    For example, Mellor et al. \cite{https://doi.org/10.48550/arxiv.2006.04647} proposed the 
    measurement of the correlation between the binary activation paterns, 
    induced by the untrained network at two inputs, named as neural architecture 
    search without training (NASWOT). The correlation is defined as the 
    logarithmic determinant of the kernel matrix, as follows:
    \begin{equation}
        s=\log\lvert K_H\rvert
    \end{equation}
    where $K_H$ is the kernel matrix.
    Later, Wu et al. \cite{10.1145/3491396.3506510} found a high score 
    obtained by such a function may not correspond to a high-performence 
    model. Thus, they additionally applied noisy immunity method on NASWOT, 
    named as noisy immunity for NASWOT (NINASWOT).
    % NTK
    For another example, Chen et al. proposed to compute the condition 
    number of neural tangent kernel (NTK) \cite{https://doi.org/10.48550/arxiv.2102.11535} 
    \cite{https://doi.org/10.48550/arxiv.2203.09137} \cite{https://doi.org/10.48550/arxiv.2109.00817}, 
    which is defined as 
    \begin{equation}
        \mathcal{K_N}=\frac{\lambda_{\textrm{max}}(\hat\Theta)}{\lambda_{\textrm{min}}(\hat\Theta)}
    \end{equation}
    and used as the score to estimate the trainability of an architecture.
	% unknown

@@

% method
    To address the problem, we propose cooperating three heterogeneous score 
    functions with genetic-based search method, we shall evaulate an architecture 
    from different aspects. More specifically, the first score function is 
    NINASWOT \cite{10.1145/3491396.3506510} as an indicator of the ability 
    to distinguish two images. The second one is the condition number of NTK 
    \cite{https://doi.org/10.48550/arxiv.2102.11535} as score to estimate the 
    trainability of an architecture. The last one is (TBD).

% conclusion
    The major contribution of this paper can be summarized as follow:
    \begin{itemize}
        \item Develope a genetic-based neural architecture search method based on three hybrid score functions.
        \item Cooperating three score functions to get a higher correlation between score and accuracy.
    \end{itemize}
    % expect what

@@

    \section{Related Works}
    In these days, the studies of training-free neural architecture search (NAS) 
    go viral, since the ability to accelerate the design of a neural network 
    architecture used on specific application, while in the same time, by using 
    training-free score function, training-free NAS cleverly avoid the drawback 
    of long-time training.

    Mellor et al. \cite{https://doi.org/10.48550/arxiv.2006.04647} proposed a 
    score function without the requirement for training. 
    Consider a mini-batch of data $X=\{x_i\}^N_{i=1}$ mapped through a neural 
    network as $f(x_i)$. The indicator variables from each ReLU units in $f$ 
    at $x_i$ form a binary code $c_i$ that define the linear region.
    The correlation between binary codes for the whole mini-batch can be examined 
    by computing the kernel matrix
    \begin{equation}
        K_H=\begin{pmatrix}N_A-d_H(c_1,c_2)&\cdots&N_A-d_H(c_1,c_N)\\\vdots&\ddots&\vdots\\N_A-d_H(c_N,c_1)&\cdots&N_A-d_H(c_N,c_1)\end{pmatrix}
    \end{equation}
    where $N_A$ is the number of ReLU units and $d_H(c_i,c_j)$ is the hamming 
    distance between the binary code $c_i$ and $c_j$.
    With the kernel matrix, the score of an architecture can be evaluate as 
    follow:
    \begin{equation}
        s=\log\lvert K_H\rvert
    \end{equation}
    The rationale behind is to see how dissimilar the linear region activated by 
    the ReLU units.

    On the other hand, Chen et al. proposed using the condition number of NTK 
    as an evaluation of the trainability, definde as
    \begin{equation}
        \mathcal{K_N}=\frac{\lambda_{\textrm{max}}(\hat\Theta)}{\lambda_{\textrm{min}}(\hat\Theta)}
    \end{equation}
    where $\lambda_{\textrm{max}}(\hat\Theta)$ and $\lambda_{\textrm{min}}(\hat\Theta)$ 
    are the maximum and minimum eigenvalues of NTK ($\hat\Theta$) respectively.
    The rationale behind is based on the work of Lee et al. \cite{Lee_2020} and 
    Xiao et al. \cite{DBLP:journals/corr/abs-1912-13053}, which concluded briefly, 
    the training dynamics of a wide neural network can be solved as 
    \begin{equation}
        \mu_t(\textbf{X}_{\textrm{train}})=(\textbf{I}-e^{-\eta\hat\Theta_{\textrm{train}}t})\textbf{Y}_{\textrm{train}}
    \end{equation}
